Maximum Entropy Spectral Analysis: a case study

### 2021-03-25 paper/mesa.tex
Edits in temperature&LIGO forecasting

We note the observed difference is always well included in the $90\%$ confidence interval: the forecasting predictions seem reliable.
On the other hand, the confidence interval is pretty large (almost as large as $\SI{15}{K}$), thus making easy for the actual data to fit the predictions. We believe that the origin of such large uncertainty is due to the complexity of the time series considered: any realistic model, even more complex than our autoregressive process, might not produce drastically lower uncertainties (in such a long term).

@@

Of course, more sophisticated forecasting methods are available in the Machine Learning literature (see e.g. \cite{LSTM_article, oord2016wavenet}) and they can be trained for precision forecasting. However, a Maximum-Entropy trained autoregressive process can be a simple baseline for comparing such more advanced methods and might suffice for many purposes.
This opens a promising path in GW data analysis and other fields of physics might also take advantage from this.

>>>>

We note the observed difference is always well included in the $90\%$ confidence interval: the forecasting predictions seem reliable.
On the other hand, the confidence interval is pretty large (almost as large as $\SI{15}{K}$), thus making ``easy" for the actual data to fit the predictions.
Indeed, the prediction model, while suitable for spectral estimation, is nothing more than a linear regression (plus noise term). Such a simple model hardly catches the complex trend in the variability of the temperature daily trend during a year. For more precise predictions, probably one should consider nonlinear regression model, tapping into the wealth of non linear predictors offered by the field of Deep Lerning.

@@

As noted above, for pushing further the prediction performance from our simple linear predictor, more sophisticated forecasting methods are available in the Machine Learning literature (see e.g. \cite{LSTM_article, oord2016wavenet}) and they can be trained for precision forecasting. However, a Maximum-Entropy trained autoregressive process can be a simple baseline for comparing such more advanced methods and might suffice for many purposes.
This opens a promising path in GW data analysis and other fields of physics might also take advantage from this.
